My Bash Notes

### 2018-12-01 Ubuntu_16.04_setup/mylinux.Rmd
up

---
title: "My Linux Notes"
subtitle: "A Quick Reference"
author: "[Yongfu Liao](https://liao961120.github.io/)"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
link-citations: yes
output:
  bookdown::html_document2:
    css: /home/liao/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 2
    toc_float:
        collapsed: false
---

@@

## Branching

### case
```bash
case "$var" in
	pattern_1)
		commands
		;;
	pattern_2)
		commands
		;;
esac
```

### if
```bash
if [[ ]]; then
	commands
elif [[ ]]; then
	commands
else
	commands
fi
```

#### pipe

```bash
[ -f <file-name> ] && <command>
[ -d <dir-name> ] || <command>
```

@@

@@

@@

@@

1. Fix floating IP
(Alternative: auto push IP address when turned on
https://superuser.com/questions/471253/ubuntu-how-to-run-a-terminal-command-on-boot)
2. Enable WakeOnLane(WOL) at BIOS: 
	1. `Power Management Setup` > `WOL: enabled`[^wol]
	2. `Power Management Setup` > `deep power off mode: disabled`[^poff]

@@

>>>>

---
title: "My Bash Notes"
subtitle: "A Quick Reference"
author: "[Yongfu Liao](https://liao961120.github.io/)"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
link-citations: yes
output:
  bookdown::html_document2:
    css: /home/liao/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 2
    toc_float:
        collapsed: false
---

@@

## case
```bash
case "$var" in
	pattern_1)
		commands
		;;
	pattern_2)
		commands
		;;
esac
```

## if
```bash
if [[ ]]; then
	commands
elif [[ ]]; then
	commands
else
	commands
fi
```

### Logical Operators

```bash
-eq # equal
-ne # not equal
-lt # less than
-le # less than or equal
-gt # greater than
-ge # greater than or equal
```

```bash
[[ $num1 -eq $num2 ]] && echo "true"
```

## Conditionals (Square brackets)

```bash
[ -f file.txt ] && echo "File exist" 
[ -s FB_title.txt ] && echo "File size > 0"
[ -d dir/ ] && echo "Dir exist"
[ -z "$var" ]      # Whether $var is empty
```

@@

## grep

Search files in working dir that contain certain string:
```bash
grep -r ".img" *
```

Search file names in working dir that contain certain string:
```bash
ls | grep ".txt"
```

## Compare Files

```bash
ls dir1 > file1.txt
ls dir2 > file2.txt
diff file1.txt file2.txt
```

@@

Reading Files
========

## Loop Over Every Line of a File
```bash
while read p; do
  date=$(echo "$p" | cut -d ',' -f 1)
  file=$(echo "$p" | cut -d ',' -f 2)
done < list.txt
```

## Loop Over Several Files
```bash
while IFS=$'\t' read -r title tags link
do
  printf "${title}/n"
  printf "${tags}/n"
  printf "${link}/n/n"
done < <(paste FB_title.txt FB_tags.txt FB_link.txt)
```

Function Flows
========

```bash
[ -f file.txt ] && exit 0
```

```bash
sleep 10 # seconds
```

@@

## Curl

```bash
curl --silent --show-error --fail https://raw.githubusercontent.com/Rbloggers/web/posts/FB_title.txt > FB_title.txt
```

- `--silent`: Don't print process to std. output
- `--show-error`: Print error message to std. output
- `--fail`: Return empty file if 404

@@

Enable WakeOnLane(WOL) at BIOS:

1. `Power Management Setup` > `WOL: enabled`[^wol]
2. `Power Management Setup` > `deep power off mode: disabled`[^poff]

@@

Other Resources
===========

- [Bash scripting cheatsheet](https://devhints.io/bash)
